---
title: "Practical Exam"
author: "Dianah Marie Canonicato"
date: "2024-03-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A. Load the built-in warpbreaks dataset.
```{r}

#1

# 1.
num_col <- sapply(warpbreaks, function(x) is.numeric(x) || is.integer(x))
print(num_col)

```

```{r}

#2. How many observations does it have?
num_observations <- nrow(warpbreaks)
print(paste("Number of observations:", num_observations))

```

```{r}
#3. Is numeric a natural data type for the columns which are stored as such? Convert to integer when necessary.
#YES
warpbreaks[, num_col] <- sapply(warpbreaks[, num_col], as.integer)
print(warpbreaks)

```

```{r}
# 4. Error messages in R sometimes report the underlying type of an object rather than the user-level class. Derive from the following code and error message what the underlying type. Explain what is the error all about. Do not just copy the error message that was displayed.
# Example code:
# my_list <- list(1, "a", TRUE)
# my_matrix <- matrix(my_list)

# The error message would be:
# Error in matrix(my_list, nrow = 3) :
#   data must be of a vector type, was 'list'

# From this error message, we can derive that the underlying type of the object 'my_list' is 'list'.
# The error message indicates that the 'matrix' function expects data to be of a vector type, but 'my_list' is of type 'list'.
# This error occurs because the 'matrix' function can only accept vectors as input, not lists.
```

B. Load the exampleFile.txt

```{r}

#1. Read the complete file using readLines.

file_path <- "/cloud/project/PractExam/exampleFile (2).txt"
lines <- readLines(file_path, warn = FALSE)
print(lines)

```

```{r}
#2. Separate the vector of lines into a vector containing comments and a vector containing the data. Hint: use grepl.

comments <- lines[grepl("^#", lines)]
print(comments)
data_lines <- lines[!grepl("^#", lines)]
print(data_lines)


```

```{r}
#3. Extract the date from the first comment line and display on the screen “It was created data.”

# Find the comment line containing the date information
date_line_index <- grep("^# Date: ", comments)

if (length(date_line_index) > 0) {
  # Extract the date from the first comment line containing the date information
  date_line <- comments[date_line_index]
  print(date_line)
  date <- gsub("# Date: ", "", date_line)
  print(date)
} else {
  print("Date information not found in the comments.")
}

```
4. Read the data into a matrix as follows.
```{r}
# a.
split_data_lines <- strsplit(data_lines, ";")
print(split_data_lines)

```

```{r}
# b.
max_fields <- max(sapply(split_data_lines, length))
print(max_fields)
split_data_lines <- lapply(split_data_lines, function(x) {
  if (length(x) < max_fields) {
    c(x, rep(NA, max_fields - length(x)))
  } else {
    x
  }
})
print(split_data_lines)

```

```{r}

# c.
data_matrix <- matrix(unlist(split_data_lines), nrow = length(split_data_lines), byrow = TRUE)
print(data_matrix)

```

```{r}
# d.
field_names_vector <- gsub("# ", "", comments[2:4])
print(field_names_vector)
dim(data_matrix)

field_names_vector<- strsplit(field_names_vector, ": ")[[1]]
print(field_names_vector)
length_field_names <- length(field_names_vector)
print(length_field_names)

if (ncol(data_matrix) == length_field_names) {
  colnames(data_matrix) <- field_names_vector
} else {
  # Handle the mismatch (adjust your code accordingly)
  print("The length of the column names does not correspond with the number of columns.")
}
```


#C. Pushing into GitHub
#1. The .rmd should be knitted into pdf form.
#2. Create a folder and named it as PractExam. The PractExam will contain the .rmd and the pdf files.
#3. Push the folder – PractExam into your GitHub repo. There is no need to change the repo. Just use the repo you have created before.


