---
title: "Untitled"
author: "Dianah Marie Canonicato"
date: "2024-02-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("dplyr")
install.packages("rvest")
install.packages("httr")
install.packages("polite")

SCRAPING FOR 50

Movie 1
```{r, warning=FALSE}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie1 <- data.frame()

for (page in 1:5) {
  link1 <- paste0("https://www.imdb.com/title/tt0903747/reviews?ref_=tt_urv", page)
  session1 <- bow(link1, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session1) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Breaking Bad (2008–2013)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie1 <- rbind(movie1, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie1)

```


Movie 2
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie2 <- data.frame()

for (page in 1:5) {
  link2 <- paste0("https://www.imdb.com/title/tt5491994/reviews?ref_=tt_urv", page)
  session2 <- bow(link2, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session2) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  movieName2 <- "Planet Earth II (2016)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".collapsable div:nth-of-type(2) .display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable span.rating-other-user-rating")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie2 <- rbind(movie2, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie = scrapedType
  ))


}

View(movie2)

```


movie3
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie3 <- data.frame()

for (page in 1:5) {
  link3 <- paste0("https://www.imdb.com/title/tt0417299/reviews?ref_=tt_urv", page)
  session3 <- bow(link3, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session3) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  movieName <- "Avatar: The Last Airbender (2005–2008)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("div.lister-item:nth-of-type(n+3) div:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable span.rating-other-user-rating")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie3 <- rbind(movie3, data.frame(
    prod_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(movie3)

```


Movie 4
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie4 <- data.frame()

for (page in 1:5) {
  link4 <- paste0("https://www.imdb.com/title/tt0111161/reviews?ref_=tt_urv", page)
  session4 <- bow(link4, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session4) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  movieName <- "The Shawshank Redemption (1994)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie4 <- rbind(movie4, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

View(movie4)

```



Movie 5
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie5 <- data.frame()

for (page in 1:5) {
  link5 <- paste0("https://www.imdb.com/title/tt0120737/reviews?ref_=tt_urv", page)
  session5 <- bow(link5, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session5) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  movieName <- "The Lord of the Rings: The Fellowship of the Ring"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie5 <- rbind(movie5, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(movie5)

```


Movie 6
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie6 <- data.frame()

for (page in 3:7) {
  link6 <- paste0("https://www.imdb.com/title/tt0468569/reviews?ref_=tt_urv", page)
  session6 <- bow(link6, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session6) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  
  movieName <- "The Dark Knight (2008)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie6 <- rbind(movie6, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
    
  ))

 

  
}

View(movie6)

```

Movie7
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie7 <- data.frame()

for (page in 3:7) {
  link7 <- paste0("https://www.imdb.com/title/tt0118799/reviews?ref_=tt_urv", page)
  session7 <- bow(link7, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session7) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  movie7 <- rbind(movie7, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
))

}

View(movie7)

```


Movie 8
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie8 <- data.frame()

for (page in 3:7) {
  link8 <- paste0("https://www.imdb.com/title/tt0047478/reviews?ref_=tt_urv", page)
  session8 <- bow(link8, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session8) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  movieName <- "Seven Samurai (1954)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

 movie8 <- rbind(movie8, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(movie8)
```

Movie9
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie9 <- data.frame()

for (page in 3:7) {
  link9 <- paste0("https://www.imdb.com/title/tt0317248/reviews?ref_=tt_urv", page)
  session9 <- bow(link9, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session9) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  movieName <- "City of God (2002)"
   scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

movie9 <- rbind(movie9, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(movie9)
```

Movie10
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie10 <- data.frame()

for (page in 6:10) {
  link10 <- paste0("https://www.imdb.com/title/tt0102926/reviews?ref_=tt_urv", page)
  session10 <- bow(link10, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session10) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "The Silence of the Lambs (1991)"
   scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

 movie10 <- rbind(movie10, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(movie10)
```

Movie11
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie11 <- data.frame()

for (page in 3:7) {
  link11 <- paste0("https://www.imdb.com/title/tt0245429/reviews?ref_=tt_urv", page)
  session11 <- bow(link11, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session11) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  movieName <- "Spirited Away (2001))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie11 <- rbind(movie11, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(movie11)
```

Movie12
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie12 <- data.frame()

for (page in 3:7) {
  link12 <- paste0("https://www.imdb.com/title/tt6751668/reviews?ref_=tt_urv", page)
  session12 <- bow(link12, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session12) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Parasite (2019)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie12 <- rbind(movie12, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

View(movie12)
```
Movie13
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie13 <- data.frame()

for (page in 3:7) {
  link13 <- paste0("https://www.imdb.com/title/tt2380307/reviews?ref_=tt_urv", page)
  session13 <- bow(link12, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session13) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Coco (I) (2017))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie13 <- rbind(movie13, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie13)
```

Movie14
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie14 <- data.frame()

for (page in 3:7) {
  link14 <- paste0("https://www.imdb.com/title/tt0053291/reviews?ref_=tt_urv", page)
  session14 <- bow(link14, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session14) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Some Like It Hot (1959)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie14 <- rbind(movie14, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie14)

```

Movie15
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie15 <- data.frame()

for (page in 3:7) {
  link15 <- paste0("https://www.imdb.com/title/tt1187043/reviews?ref_=tt_urv", page)
  session15 <- bow(link15, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session15) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "3 Idiots (2009)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie15 <- rbind(movie15, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie15)

```

Movie16
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie16 <- data.frame()

for (page in 3:7) {
  link16 <- paste0("https://www.imdb.com/title/tt0105236/reviews?ref_=tt_urv", page)
  session16 <- bow(link16, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session16) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Reservoir Dogs (1992)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie16 <- rbind(movie16, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie16)


```

Movie17
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie17 <- data.frame()

for (page in 3:7) {
  link17 <- paste0("https://www.imdb.com/title/tt0036775/reviews?ref_=tt_urv", page)
  session17 <- bow(link17, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session17) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Double Indemnity (1944)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie17 <- rbind(movie17, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie17)


```

Movie18
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie18 <- data.frame()

for (page in 3:7) {
  link18 <- paste0("https://www.imdb.com/title/tt26047818/reviews?ref_=tt_urv", page)
  session18 <- bow(link18, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session18) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Anyone But You (2023))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie18 <- rbind(movie18, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie18)


```

Movie19
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie19 <- data.frame()

for (page in 3:7) {
  link19 <- paste0("https://www.imdb.com/title/tt0211915/reviews?ref_=tt_urv", page)
  session19 <- bow(link19, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session19) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Amélie (2001)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie19 <- rbind(movie19, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie19)

```
Movie20

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie20 <- data.frame()

for (page in 3:7) {
  link20 <- paste0("https://www.imdb.com/title/tt0133093/reviews?ref_=tt_urv", page)
  session20 <- bow(link20, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session20) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "The Matrix (1999))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie20 <- rbind(movie20, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie20)
```

Movie21

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie21  <- data.frame()

for (page in 3:7) {
  link21 <- paste0("https://www.imdb.com/title/tt11762114/reviews?ref_=tt_urv", page)
  session21 <- bow(link21, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session21) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Mean Girls (2024))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie21 <- rbind(movie21, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie21)
```

Movie22
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie22  <- data.frame()

for (page in 3:7) {
  link22 <- paste0("https://www.imdb.com/title/tt0110912/reviews?ref_=tt_urv", page)
  session22 <- bow(link22, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session22) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Pulp Fiction (1994))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie22 <- rbind(movie22, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie22)

```

movie23
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie23  <- data.frame()

for (page in 3:7) {
  link23 <- paste0("https://www.imdb.com/title/tt6751668/reviews?ref_=tt_urv", page)
  session23 <- bow(link23, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session23) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Parasite (2019))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie23 <- rbind(movie23, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie23)

```

movie24
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie24  <- data.frame()

for (page in 3:7) {
  link24  <- paste0("https://www.imdb.com/title/tt0044741/reviews?ref_=tt_urv", page)
  session24  <- bow(link24 , user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session24 ) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Ikiru (1952))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie24 <- rbind(movie24, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie24)

```

movie25
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie25  <- data.frame()

for (page in 3:7) {
  link25  <- paste0("https://www.imdb.com/title/tt0088763/reviews?ref_=tt_urv", page)
  session25 <- bow(link25 , user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session25) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Back to the Future (1985))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie25 <- rbind(movie25, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie25)

```

movie26
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie26  <- data.frame()

for (page in 3:7) {
  link26  <- paste0("https://www.imdb.com/title/tt0167404/reviews?ref_=tt_urv", page)
  session26 <- bow(link26 , user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session26) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "The Sixth Sense (1999))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie26 <- rbind(movie26, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie26)

```

movie27
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie27  <- data.frame()

for (page in 3:7) {
  link27  <- paste0("https://www.imdb.com/title/tt15239678/reviews?ref_=tt_urv", page)
  session27 <- bow(link27 , user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session27) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Dune: Part Two (2024))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie27 <- rbind(movie27, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie27)

```

movie28
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie28  <- data.frame()

for (page in 3:7) {
  link28  <- paste0("https://www.imdb.com/title/tt14230458/reviews?ref_=tt_urv", page)
  session28 <- bow(link28, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session28) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Poor Things (2023))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie28 <- rbind(movie28, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie28)

```

movie29
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie29  <- data.frame()

for (page in 3:7) {
  link29  <- paste0("https://www.imdb.com/title/tt15398776/reviews?ref_=tt_urv", page)
  session29 <- bow(link29, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session29) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Oppenheimer (I) (2023))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie29 <- rbind(movie29, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie29)

```

movie30
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie30  <- data.frame()

for (page in 3:7) {
  link30  <- paste0("https://www.imdb.com/title/tt0047478/reviews?ref_=tt_urv", page)
  session30 <- bow(link30, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session30) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Seven Samurai (1954)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie30 <- rbind(movie30, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie30)

```

movie31
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie31  <- data.frame()

for (page in 3:7) {
  link31  <- paste0("https://www.imdb.com/title/tt7160372/reviews?ref_=tt_urv", page)
  session31 <- bow(link31, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session31) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "The Zone of Interest (2023))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie31 <- rbind(movie31, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie31)

```

movie32
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie32  <- data.frame()

for (page in 3:7) {
  link32  <- paste0("https://www.imdb.com/title/tt11097384/reviews?ref_=tt_urv", page)
  session32 <- bow(link32, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session32) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Spaceman (I) (2024))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie32 <- rbind(movie32, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie32)

```

movie33
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie33  <- data.frame()

for (page in 3:7) {
  link33  <- paste0("https://www.imdb.com/title/tt26861992/reviews?ref_=tt_urv", page)
  session33 <- bow(link33, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session33) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Mea Culpa (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie33 <- rbind(movie33, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie33)

```

movie34
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie34  <- data.frame()

for (page in 3:7) {
  link34  <- paste0("https://www.imdb.com/title/tt0087182/reviews?ref_=tt_urv", page)
  session34 <- bow(link34, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session34) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "Dune (1984)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie34 <- rbind(movie34, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie34)

```

movie35
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie35  <- data.frame()

for (page in 3:7) {
  link35  <- paste0("https://www.imdb.com/title/tt14849194/reviews?ref_=tt_urv", page)
  session35 <- bow(link35, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session35) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

 movieName <- "The Holdovers (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes(".display-name-link a")[1:10]
  scrapedReview <- scrapeNodes("span.spoiler-warning, div.content:nth-of-type(3) div.text")[1:10]
  scrapedDate <- scrapeNodes("span.review-date")[1:10]
  scrapedRating <- scrapeNodes(".collapsable div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]


movie35 <- rbind(movie35, data.frame(
    movie_name = movieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(movie35)

```
Movie 36

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie36 <- data.frame()

for (page in 3:7) {
  link36 <- paste0("https://www.imdb.com/title/tt17351924/reviews?ref_=tt_urv", page)
  session36 <- bow(link36, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session36) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Saltburn (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie36 <- rbind(movie36, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie36)

```

Movie 37

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie37 <- data.frame()

for (page in 1:5) {
  link37 <- paste0("https://www.imdb.com/title/tt21192142/reviews?ref_=tt_urv", page)
  session37 <- bow(link37, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session37) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "All of Us Strangers (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie37 <- rbind(movie37, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie37)

```

movie38

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie38 <- data.frame()

for (page in 1:5) {
  link38 <- paste0("https://www.imdb.com/title/tt1563738/reviews?ref_=tt_urv", page)
  session38 <- bow(link38, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session38) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "One Day (2011)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie38 <- rbind(movie38, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie38)

```

movie39

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie39 <- data.frame()

for (page in 1:5) {
  link39 <- paste0("https://www.imdb.com/title/tt6259380/reviews?ref_=tt_urv", page)
  session39 <- bow(link39, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session39) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Code 8 (2019)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie39 <- rbind(movie39, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie39)

```


movie40

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie40 <- data.frame()

for (page in 1:5) {
  link40 <- paste0("https://www.imdb.com/title/tt19356262/reviews?ref_=tt_urv", page)
  session40 <- bow(link40, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session40) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Drive-Away Dolls (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie40 <- rbind(movie40, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie40)

```

movie41

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie41 <- data.frame()

for (page in 1:5) {
  link41 <- paste0("https://www.imdb.com/title/tt17009710/reviews?ref_=tt_urv", page)
  session41 <- bow(link41, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session41) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Anatomy of a Fall (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie41 <- rbind(movie41, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie41)

```

movie42

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie42 <- data.frame()

for (page in 1:5) {
  link42 <- paste0("https://www.imdb.com/title/tt9663764/reviews?ref_=tt_urv", page)
  session42 <- bow(link42, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session42) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Aquaman and the Lost Kingdom (2023))"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie42 <- rbind(movie42, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie42)

```

movie43

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie43 <- data.frame()

for (page in 1:5) {
  link43 <- paste0("https://www.imdb.com/title/tt21188080/reviews?ref_=tt_urv", page)
  session43 <- bow(link43, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session43) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Lisa Frankenstein (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie43 <- rbind(movie43, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie43)

```

movie44

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie44 <- data.frame()

for (page in 1:5) {
  link44 <- paste0("https://www.imdb.com/title/tt8521778/reviews?ref_=tt_urv", page)
  session44 <- bow(link44, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session44) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Bob Marley: One Love (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie44 <- rbind(movie44, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie44)

```

movie45

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie45 <- data.frame()

for (page in 1:5) {
  link45 <- paste0("https://www.imdb.com/title/tt21064584/reviews?ref_=tt_urv", page)
  session45 <- bow(link45, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session45) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "The Iron Claw (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie45 <- rbind(movie45, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie45)

```

movie46

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie46 <- data.frame()

for (page in 1:5) {
  link46 <- paste0("https://www.imdb.com/title/tt5537002/reviews?ref_=tt_urv", page)
  session46 <- bow(link46, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session46) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Killers of the Flower Moon (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie46 <- rbind(movie46, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie46)

```

movie47

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie47 <- data.frame()

for (page in 1:5) {
  link47 <- paste0("https://www.imdb.com/title/tt15314262/reviews?ref_=tt_urv", page)
  session47 <- bow(link47, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session47) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "The Beekeeper (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie47 <- rbind(movie47, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie47)

```

movie48

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie48 <- data.frame()

for (page in 1:5) {
  link48 <- paste0("https://www.imdb.com/title/tt23561236/reviews?ref_=tt_urv", page)
  session48 <- bow(link48, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session48) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "American Fiction (2023)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie48 <- rbind(movie48, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie48)

```

movie49

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie49 <- data.frame()

for (page in 1:5) {
  link49 <- paste0("https://www.imdb.com/title/tt15009428/reviews?ref_=tt_urv", page)
  session49 <- bow(link49, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session49) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Argylle (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie49 <- rbind(movie49, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
  ))

  
}

View(movie49)

```

movie50

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

movie50 <- data.frame()

for (page in 1:5) {
  link50 <- paste0("https://www.imdb.com/title/tt8310486/reviews?ref_=tt_urv", page)
  session50 <- bow(link50, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session50) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  MovieName <- "Miller's Girl (2024)"
  scrapedTitle <- scrapeNodes("a.title")[1:10]
  scrapedReviewer <- scrapeNodes("div.display-name-date:nth-of-type(2) a")[1:10]
  scrapedReview <- scrapeNodes("div.collapsable:nth-of-type(n+2) div.text, div:nth-of-type(n+15) span.spoiler-warning")[1:10]
  scrapedDate <- scrapeNodes("div.display-name-date:nth-of-type(2) span.review-date")[1:10]
  scrapedRating <- scrapeNodes("div.ipl-ratings-bar")[1:10]
  scrapedType <- scrapeNodes(".sc-ab73d3b3-1 a.ipc-metadata-list-item__list-content-item")[1:10]

movie50 <- rbind(movie50, data.frame(
    movie_name = MovieName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_movie= scrapedType
    
  ))

  
}

View(movie50)

```

```{r}
all_movies <- data.frame()
col_names <- c("Movie Title", "Review Title", "Reviewer", "Review", "Date", "Ratings", "Type Of Movies")
for (i in 1:50) {
  assign(paste0("movie", i), `colnames<-`(get(paste0("movie", i)), col_names))
  all_movies <- rbind(all_movies, get(paste0("movie", i)))
}
View(all_movies)
tail(all_movies)
write.csv(all_movies, file= "AllMovies.csv",)

```




